Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
tidied up contributions; misc other updates

We make the following contributions in this paper.
\begin{itemize}
\item
The design of the Marlowe language.
\item
An executable, small-step semantics of Marlowe in Haskell.
\item 
Extending Marlowe's expressibility by embedding it as a Haskell \haskellinline{data} type.
\item
The Meadow tool that allows users to interact with and simulate the operation of embedded Marlowe contracts. 
\end{itemize}

>>>>

We make the following contributions in this paper.
\begin{itemize}
\item
Designing a DSL for financial contracts on blockchains: Marlowe.
\item
Defining an executable, small-step semantics of Marlowe in Haskell.
\item 
Embedding Marlowe as a Haskell \haskellinline{data} type to extend its expressibility.
\item
Developing the Meadow tool that allows users to interact with and simulate the operation of embedded Marlowe contracts. 
\end{itemize}
